sensiAnPaper1All

### 2016-03-01 paper1_results_figs.Rmd
name changes from mix1,2,3 to mix 1,adaptive,2

# Figures for paper 1 
# version 4 - in progress

@@

  #2) mixture1 : time to resistance for either insecticide when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for EITHER insecticide in mixture  
  resistPointsMix1 <- findResistancePoints(listOutMix, locus='either')  
  #todo - to be comparable I think this should be for when resistance to BOTH insecticides is reached

  #3) mixture2 : when resistance to one insecticide in the mixture reached, switch to sole use of the 
  #   other until that too reaches the critical point. Record total time.
  # what I actually need to do is start with mixture find the first critical point
  # (need to know which of the insecticides it is)
  # then I need to go to the single run for the other insecticide & starting at 
  # it's current resistance point find out how many more generations to go
  #inputs : inAndOutI1, inAndOutI2, inAndOutMix
  resistPointsMix2 <- findResistancePointsMixResponsive(listOutMix, listOutI1, listOutI2)

  #4) mixture3 : time to resistance for both insecticides when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for BOTH insecticide in mixture  
  resistPointsMix3 <- findResistancePoints(listOutMix, locus='both')

@@

  resistPointsI1_T <- addStrategyColumn(resistPointsI1,"insecticide 1",ggInput) 
  resistPointsI2_T <- addStrategyColumn(resistPointsI2,"insecticide 2",ggInput)   
  resistPointsSeq_T <- addStrategyColumn(resistPointsSeq,"Sequential",ggInput) 
  resistPointsMix1_T <- addStrategyColumn(resistPointsMix1,"Mixture 1",ggInput) 
  resistPointsMix2_T <- addStrategyColumn(resistPointsMix2,"Mixture 2",ggInput) 
  resistPointsMix3_T <- addStrategyColumn(resistPointsMix3,"Mixture 3",ggInput)

  ggInsOuts <- rbind( resistPointsI1_T, resistPointsI2_T, resistPointsSeq_T, 
                      resistPointsMix1_T, resistPointsMix2_T, resistPointsMix3_T)

@@

  #format data in a different way to enable PRCC on difference between sequential & mix2
  #resistPointsMix2_T
  #resistPointsSeq_T

  #columns to remove from first
  indices1 <- which(names(resistPointsMix2_T) %in% c("gen_cP0.1","gen_cP0.5","strategy"))
  #columns to add to 2nd  
  indices2 <- which(names(resistPointsMix2_T) %in% c("gen_cP0.25"))  
  #rename column in 2nd
  tmp <- resistPointsSeq_T[indices2]
  names(tmp) <- "gen_cP0.25seq"

  df_diff <- cbind(resistPointsMix2_T[-indices1], tmp)

@@

  print( ggplot(ggSubset, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian( ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) +
      #scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mixture 1","Sequential","Mixture 2","Mixture 3"), labels = c("insecticide 1"="Sole use", "Mixture 1"="1st in mix","Sequential"="2nd in sequence", "Mixture 2"="2nd in mix\nswitch to sole", "Mixture 3"="2nd in mix" ) )
      scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mixture 1","Sequential","Mixture 2","Mixture 3"), labels = c("insecticide 1"="Sole use", "Mixture 1"="1st in mix","Sequential"="2nd in sequence", "Mixture 2"="adaptive mix", "Mixture 3"="2nd in mix" ) )

@@

# Some examples showing how changing effectiveness can alter the ranking of insecticide strategies
### Curtis' Fig 2. inputs : mix2 > combined > mix1 > seq
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### decrease effectiveness of I2 from 1 to 0.85 : mix2 > combined > seq > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### also decrease effectiveness of I1 from 0.73 to 0.63 : seq > mix2 > combined > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.63 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

# PRCC difference in time-to-resistance between sequential and mixture2
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

>>>>

# Figures for paper 1 
# version 5 - in progress

@@

  #2) mixture1 : time to resistance for either insecticide when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for EITHER insecticide in mixture  
  resistPointsMix_1 <- findResistancePoints(listOutMix, locus='either')  
  #todo - to be comparable I think this should be for when resistance to BOTH insecticides is reached

  #3) mixture2 : when resistance to one insecticide in the mixture reached, switch to sole use of the 
  #   other until that too reaches the critical point. Record total time.
  # what I actually need to do is start with mixture find the first critical point
  # (need to know which of the insecticides it is)
  # then I need to go to the single run for the other insecticide & starting at 
  # it's current resistance point find out how many more generations to go
  #inputs : inAndOutI1, inAndOutI2, inAndOutMix
  resistPointsMix_A <- findResistancePointsMixResponsive(listOutMix, listOutI1, listOutI2)

  #4) mixture3 : time to resistance for both insecticides when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for BOTH insecticide in mixture  
  resistPointsMix_2 <- findResistancePoints(listOutMix, locus='both')

@@

  resistPointsI1_T <- addStrategyColumn(resistPointsI1,"insecticide 1",ggInput) 
  resistPointsI2_T <- addStrategyColumn(resistPointsI2,"insecticide 2",ggInput)   
  resistPointsSeq_T <- addStrategyColumn(resistPointsSeq,"Sequential",ggInput) 
  resistPointsMix_1_T <- addStrategyColumn(resistPointsMix_1,"Mix either",ggInput) 
  resistPointsMix_A_T <- addStrategyColumn(resistPointsMix_A,"Mix adaptive",ggInput) 
  resistPointsMix_2_T <- addStrategyColumn(resistPointsMix_2,"Mix both",ggInput)

  ggInsOuts <- rbind( resistPointsI1_T, resistPointsI2_T, resistPointsSeq_T, 
                      resistPointsMix_1_T, resistPointsMix_A_T, resistPointsMix_2_T)

@@

  #format data in a different way to enable PRCC on difference between sequential & mix2
  #resistPointsMix_A_T
  #resistPointsSeq_T

  #columns to remove from first
  indices1 <- which(names(resistPointsMix_A_T) %in% c("gen_cP0.1","gen_cP0.5","strategy"))
  #columns to add to 2nd  
  indices2 <- which(names(resistPointsMix_A_T) %in% c("gen_cP0.25"))  
  #rename column in 2nd
  tmp <- resistPointsSeq_T[indices2]
  names(tmp) <- "gen_cP0.25seq"

  df_diff <- cbind(resistPointsMix_A_T[-indices1], tmp)

@@

  print( ggplot(ggSubset, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian( ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) +
      #scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Sole use", "Mix either"="1st in mix","Sequential"="2nd in sequence", "Mix adaptive"="2nd in mix\nswitch to sole", "Mix both"="2nd in mix" ) )
      scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Sole use", "Mix either"="1st in mix","Sequential"="2nd in sequence", "Mix adaptive"="adaptive mix", "Mix both"="2nd in mix" ) )

@@

# Some examples showing how changing effectiveness can alter the ranking of insecticide strategies
### Curtis' Fig 2. inputs : mix2 > adaptive > mix1 > seq
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### decrease effectiveness of I2 from 1 to 0.85 : mix2 > adaptive > seq > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

### also decrease effectiveness of I1 from 0.73 to 0.63 : seq > mix2 > adaptive > mix1
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.63 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )
```

# PRCC difference in time-to-resistance between sequential and mixture adaptive
```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=3.5}

### 2016-03-01 sensiAnPaper1All.Rmd
name changes from mix1,2,3 to mix 1,adaptive,2

```{r, eval=FALSE}
  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

@@

  ## is mix1 better than sequential ?
  #T/F
  resistBetterMix1SeqBoolean <- resistPointsMix1 > resistPointsSeq
  #convert to 0/1
  resistBetterMix1Seq <- plyr::aaply(resistBetterMix1SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix1Seq) <- gsub('gen','betterMix1Seq', rownames(resistBetterMix1Seq))

  rowSums(resistBetterMix1Seq)/ncol(resistBetterMix1Seq)
  #100runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #                .25                   .26                   .30   
  #1000runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #               .178                  .232                  .238 
  #new100
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #              0.18                 0.24                 0.25 
  #new1000
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #             0.223                0.245                0.243

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix2SeqBoolean <- resistPointsMix2 > resistPointsSeq
  #convert to 0/1
  resistBetterMix2Seq <- plyr::aaply(resistBetterMix2SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix2Seq) <- gsub('gen','betterMix2Seq', rownames(resistBetterMix2Seq))

  rowSums(resistBetterMix2Seq)/ncol(resistBetterMix2Seq)  
  #1000runs
  #betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
  #             0.471                0.568                0.551 
  #new100
  #betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
  #              0.58                 0.57                 0.52 
  #new1000
  #betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
  #             0.558                0.563                0.534

  ## is mix3 better than sequential ?
  #T/F
  resistBetterMix3SeqBoolean <- resistPointsMix3 > resistPointsSeq
  #convert to 0/1
  resistBetterMix3Seq <- plyr::aaply(resistBetterMix3SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix3Seq) <- gsub('gen','betterMix3Seq', rownames(resistBetterMix3Seq))

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix3Seq)/ncol(resistBetterMix3Seq)
  #100runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                  .83                   .75                   .72 
  #1000runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                .794                  .726                  .673  
  #new100
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #              0.83                 0.79                 0.72 
  #new1000
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #             0.820                0.747                0.677

@@

  #check2
#   #what is the absolute difference between mix3 & sequential ?
#   resistDifferenceMix3Seq <- resistPointsMix3 - resistPointsSeq
#   
#   #check3 is their a difference between the mix & the individual strategies
#   #looks mostly plausible, occasionally there are 0s
#   resistDifferenceMix1I1 <- resistPointsMix1 - resistPointsI1
#   resistDifferenceMix1I2 <- resistPointsMix1 - resistPointsI2

@@

  ## is mix1 better than sequential ?
  #T/F
  resistBetterMix1SeqBoolean20 <- resistPointsMix1 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix1Seq20 <- plyr::aaply(resistBetterMix1SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix1Seq20) <- gsub('gen','betterMix1Seq20', rownames(resistBetterMix1Seq20))

  rowSums(resistBetterMix1Seq20)/ncol(resistBetterMix1Seq20)
  #1000runs
 #betterMix1Seq20_cP0.1 betterMix1Seq20_cP0.25  betterMix1Seq20_cP0.5 
 #                 0.136                  0.175                  0.173 
  #new1000
 #betterMix1Seq20_cP0.1 betterMix1Seq20_cP0.25  betterMix1Seq20_cP0.5 
#                 0.163                  0.178                  0.182

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix2SeqBoolean20 <- resistPointsMix2 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix2Seq20 <- plyr::aaply(resistBetterMix2SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix2Seq20) <- gsub('gen','betterMix2Seq20', rownames(resistBetterMix2Seq20))

  rowSums(resistBetterMix2Seq20)/ncol(resistBetterMix2Seq20)  
  #1000runs
#  betterMix2Seq20_cP0.1 betterMix2Seq20_cP0.25  betterMix2Seq20_cP0.5 
#                  0.241                  0.326                  0.313 
  #new1000
# betterMix2Seq20_cP0.1 betterMix2Seq20_cP0.25  betterMix2Seq20_cP0.5 
#                 0.283                  0.302                  0.283

  ## is mix3 better than sequential ?
  #T/F
  resistBetterMix3SeqBoolean20 <- resistPointsMix3 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix3Seq20 <- plyr::aaply(resistBetterMix3SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix3Seq20) <- gsub('gen','betterMix3Seq20', rownames(resistBetterMix3Seq20))

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix3Seq20)/ncol(resistBetterMix3Seq20)
  #1000runs
#  betterMix3Seq20_cP0.1 betterMix3Seq20_cP0.25  betterMix3Seq20_cP0.5 
#                  0.672                  0.560                  0.488   
  #new1000
# betterMix3Seq20_cP0.1 betterMix3Seq20_cP0.25  betterMix3Seq20_cP0.5 
#                 0.622                  0.536                  0.458

@@

  resistBetterMix1Seq <- repMix(resistBetterMix1Seq)
  resistBetterMix2Seq <- repMix(resistBetterMix2Seq)
  resistBetterMix3Seq <- repMix(resistBetterMix3Seq)

  resistBetterMix1Seq20 <- repMix(resistBetterMix1Seq20)
  resistBetterMix2Seq20 <- repMix(resistBetterMix2Seq20)
  resistBetterMix3Seq20 <- repMix(resistBetterMix3Seq20)

  #bind results onto predictors
  treeInput <- rbind( treeInput, resistBetterMix1Seq )
  treeInput <- rbind( treeInput, resistBetterMix2Seq )
  treeInput <- rbind( treeInput, resistBetterMix3Seq )
  #add >20% results
  treeInput <- rbind( treeInput, resistBetterMix1Seq20 )
  treeInput <- rbind( treeInput, resistBetterMix2Seq20 )
  treeInput <- rbind( treeInput, resistBetterMix3Seq20 )

@@

  treeResponses <- c( rownames(resistBetterMix1Seq),
                      rownames(resistBetterMix2Seq),
                      rownames(resistBetterMix3Seq),
                      rownames(resistBetterMix1Seq20),
                      rownames(resistBetterMix2Seq20),
                      rownames(resistBetterMix3Seq20)
                      )

@@

    treeResponse <- "betterMix2Seq_cP0.5"

@@

    #comparing it with 0/1 gives the same big tree
    treeInput$betterMix2Seq_cP0.5numeric <- as.numeric(treeInput$betterMix2Seq_cP0.5)

    treeResponse <- "betterMix2Seq_cP0.5numeric"

@@

```    
#   treeResponse <- 'betterMix1Seq_cP0.5'
#   tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
#   
#   #if get error number of rows of matrices must match (see arg 2)
#   #is because all vals are 0
# 
#   plot(tree) #plots tree
#   text(tree) #labels tree
#   #branch predictors 2 phis & P_2  
#     
#   #for mix3 (resistance to both)
#   x11()
#   treeResponse <- 'betterMix3Seq_cP0.5'
#   tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class')  
#   plot(tree) #plots tree
#   text(tree) #labels tree  
#   
#   #branch predictors 2 phis & P_1
#   
#   #or from rpart.plot
#   #prp(tree)
#   
#   #adds in no. scenarios correctly and incorrectly classified
#   prp(tree, extra=1, varlen = 10, main=treeResponse)
#   savePlot(paste0(outFolder,"tree",treeResponse,".png"), type='png')

>>>>

```{r, eval=TRUE}
  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

@@

  ## is mix1 better than sequential ?
  #T/F
  resistBetterMix_1SeqBoolean <- resistPointsMix_1 > resistPointsSeq
  #convert to 0/1
  resistBetterMix_1Seq <- plyr::aaply(resistBetterMix_1SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_1Seq) <- gsub('gen','betterMix_1Seq', rownames(resistBetterMix_1Seq))

  rowSums(resistBetterMix_1Seq)/ncol(resistBetterMix_1Seq)
  #100runs
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #                .25                   .26                   .30   
  #1000runs
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #               .178                  .232                  .238 
  #new100
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #              0.18                 0.24                 0.25 
  #new1000
  #betterMix_1Seq_cP0.1 betterMix_1Seq_cP0.25  betterMix_1Seq_cP0.5 
  #             0.223                0.245                0.243

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix_ASeqBoolean <- resistPointsMix_A > resistPointsSeq
  #convert to 0/1
  resistBetterMix_ASeq <- plyr::aaply(resistBetterMix_ASeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_ASeq) <- gsub('gen','betterMix_ASeq', rownames(resistBetterMix_ASeq))

  rowSums(resistBetterMix_ASeq)/ncol(resistBetterMix_ASeq)  
  #1000runs
  #betterMix_ASeq_cP0.1 betterMix_ASeq_cP0.25  betterMix_ASeq_cP0.5 
  #             0.471                0.568                0.551 
  #new100
  #betterMix_ASeq_cP0.1 betterMix_ASeq_cP0.25  betterMix_ASeq_cP0.5 
  #              0.58                 0.57                 0.52 
  #new1000
  #betterMix_ASeq_cP0.1 betterMix_ASeq_cP0.25  betterMix_ASeq_cP0.5 
  #             0.558                0.563                0.534

  ## is mix3 better than sequential ?
  #T/F
  resistBetterMix_2SeqBoolean <- resistPointsMix_2 > resistPointsSeq
  #convert to 0/1
  resistBetterMix_2Seq <- plyr::aaply(resistBetterMix_2SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_2Seq) <- gsub('gen','betterMix_2Seq', rownames(resistBetterMix_2Seq))

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix_2Seq)/ncol(resistBetterMix_2Seq)
  #100runs
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #                  .83                   .75                   .72 
  #1000runs
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #                .794                  .726                  .673  
  #new100
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #              0.83                 0.79                 0.72 
  #new1000
  #betterMix_2Seq_cP0.1 betterMix_2Seq_cP0.25  betterMix_2Seq_cP0.5 
  #             0.820                0.747                0.677

@@

  #check2
#   #what is the absolute difference between mix3 & sequential ?
#   resistDifferenceMix_2Seq <- resistPointsMix_2 - resistPointsSeq
#   
#   #check3 is their a difference between the mix & the individual strategies
#   #looks mostly plausible, occasionally there are 0s
#   resistDifferenceMix_1I1 <- resistPointsMix_1 - resistPointsI1
#   resistDifferenceMix_1I2 <- resistPointsMix_1 - resistPointsI2

@@

  ## is mix1 better than sequential ?
  #T/F
  resistBetterMix_1SeqBoolean20 <- resistPointsMix_1 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix_1Seq20 <- plyr::aaply(resistBetterMix_1SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_1Seq20) <- gsub('gen','betterMix_1Seq20', rownames(resistBetterMix_1Seq20))

  rowSums(resistBetterMix_1Seq20)/ncol(resistBetterMix_1Seq20)
  #1000runs
 #betterMix_1Seq20_cP0.1 betterMix_1Seq20_cP0.25  betterMix_1Seq20_cP0.5 
 #                 0.136                  0.175                  0.173 
  #new1000
 #betterMix_1Seq20_cP0.1 betterMix_1Seq20_cP0.25  betterMix_1Seq20_cP0.5 
#                 0.163                  0.178                  0.182

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix_ASeqBoolean20 <- resistPointsMix_A > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix_ASeq20 <- plyr::aaply(resistBetterMix_ASeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_ASeq20) <- gsub('gen','betterMix_ASeq20', rownames(resistBetterMix_ASeq20))

  rowSums(resistBetterMix_ASeq20)/ncol(resistBetterMix_ASeq20)  
  #1000runs
#  betterMix_ASeq20_cP0.1 betterMix_ASeq20_cP0.25  betterMix_ASeq20_cP0.5 
#                  0.241                  0.326                  0.313 
  #new1000
# betterMix_ASeq20_cP0.1 betterMix_ASeq20_cP0.25  betterMix_ASeq20_cP0.5 
#                 0.283                  0.302                  0.283

  ## is mix3 better than sequential ?
  #T/F
  resistBetterMix_2SeqBoolean20 <- resistPointsMix_2 > (1.2 * resistPointsSeq)
  #convert to 0/1
  resistBetterMix_2Seq20 <- plyr::aaply(resistBetterMix_2SeqBoolean20,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix_2Seq20) <- gsub('gen','betterMix_2Seq20', rownames(resistBetterMix_2Seq20))

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix_2Seq20)/ncol(resistBetterMix_2Seq20)
  #1000runs
#  betterMix_2Seq20_cP0.1 betterMix_2Seq20_cP0.25  betterMix_2Seq20_cP0.5 
#                  0.672                  0.560                  0.488   
  #new1000
# betterMix_2Seq20_cP0.1 betterMix_2Seq20_cP0.25  betterMix_2Seq20_cP0.5 
#                 0.622                  0.536                  0.458

@@

  resistBetterMix_1Seq <- repMix(resistBetterMix_1Seq)
  resistBetterMix_ASeq <- repMix(resistBetterMix_ASeq)
  resistBetterMix_2Seq <- repMix(resistBetterMix_2Seq)

  resistBetterMix_1Seq20 <- repMix(resistBetterMix_1Seq20)
  resistBetterMix_ASeq20 <- repMix(resistBetterMix_ASeq20)
  resistBetterMix_2Seq20 <- repMix(resistBetterMix_2Seq20)

  #bind results onto predictors
  treeInput <- rbind( treeInput, resistBetterMix_1Seq )
  treeInput <- rbind( treeInput, resistBetterMix_ASeq )
  treeInput <- rbind( treeInput, resistBetterMix_2Seq )
  #add >20% results
  treeInput <- rbind( treeInput, resistBetterMix_1Seq20 )
  treeInput <- rbind( treeInput, resistBetterMix_ASeq20 )
  treeInput <- rbind( treeInput, resistBetterMix_2Seq20 )

@@

  treeResponses <- c( rownames(resistBetterMix_1Seq),
                      rownames(resistBetterMix_ASeq),
                      rownames(resistBetterMix_2Seq),
                      rownames(resistBetterMix_1Seq20),
                      rownames(resistBetterMix_ASeq20),
                      rownames(resistBetterMix_2Seq20)
                      )

@@

    treeResponse <- "betterMix_ASeq_cP0.5"

@@

    #comparing it with 0/1 gives the same big tree
    treeInput$betterMix_ASeq_cP0.5numeric <- as.numeric(treeInput$betterMix_ASeq_cP0.5)

    treeResponse <- "betterMix_ASeq_cP0.5numeric"

@@

```    
#   treeResponse <- 'betterMix_1Seq_cP0.5'
#   tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
#   
#   #if get error number of rows of matrices must match (see arg 2)
#   #is because all vals are 0
# 
#   plot(tree) #plots tree
#   text(tree) #labels tree
#   #branch predictors 2 phis & P_2  
#     
#   #for mix3 (resistance to both)
#   x11()
#   treeResponse <- 'betterMix_2Seq_cP0.5'
#   tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class')  
#   plot(tree) #plots tree
#   text(tree) #labels tree  
#   
#   #branch predictors 2 phis & P_1
#   
#   #or from rpart.plot
#   #prp(tree)
#   
#   #adds in no. scenarios correctly and incorrectly classified
#   prp(tree, extra=1, varlen = 10, main=treeResponse)
#   savePlot(paste0(outFolder,"tree",treeResponse,".png"), type='png')
